### 2020-03-17 short.body.tex
Update short.body.tex

There is significant ongoing interest in asymptomatic infections in COVID-19 \citep{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \citep{bai2020presumed} for two major reasons.
First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
Given that 86\% of the cases were undocumted in Wuhan prior to travel restriction and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play important role in the transmission of COVID-19.

>>>>

There is significant ongoing interest in asymptomatic infections in COVID-19 \citep{chan2020familial, pan2020asymptomatic, tangearly} and their transmission potential \citep{bai2020presumed} for two major reasons.
First, the proportion of infections that are asymptomatic (see~\citep{mizumoto_2020}) is critical to attempts to estimate the likely burden of severe outcomes (including mortality \citep{fauci_nejm2020}) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts \citep{fraser2004factors}.
Given that 86\% of the cases were undocumented in Wuhan prior to travel restrictions and may account for 79\% of infection of severe, symptomatic cases \citep{Lieabb3221}, asymptomatic cases are also likely to play an important role in the transmission of COVID-19.
